\section{\sc Additional Experience}

{\bf{Outreach}}\\
\begin{itemize}
\setlength\itemsep{0em}
\item GW170104 reddit AMA organizer/participant, Max Planck Institute for Gravitational Physics, (Spring 2017)
\item Zukunftstag (future day) demonstrator, Max Planck Institute for Gravitational Physics. (Spring 2017)
\item March for Science participant, G{\"o}ttingen, Germany. (Spring 2017) 
\item Spooky Physics Open House organizer/participant, University of Mississippi. (2012-2016)
\item Physics demo shows organizer/participant, Oxford Elementary. (2012-2016)
\item Science Cafe presenter, University of Texas Rio Grande Valley. (July 2015)
\item Nerd Night volunteer, Brownsville, TX. (June-July 2015)
\item Physics Circus volunteer, University of Texas Rio Grande Valley SPS. (June 2015)
\end{itemize}

{\bf{Teaching}}\\
\begin{itemize}
\setlength\itemsep{0em}
\item Astronomy 1 Teaching Assistant, University of Glasgow. (Spring 2018)
\item Phys 108 Lab Teaching Assistant, University of Mississippi. (Spring 2016)
\item LIBA 150 interdisciplinary science course Teaching Assistant, University of Mississippi. (Fall 2015)
\end{itemize}

{\bf{Leadership}}\\
\begin{itemize}
\setlength\itemsep{0em}
\item Library Ambassador, University of Mississippi. (06/2012 - 2016)
\item Vice President, Beta Beta Chapter of Beta Theta Pi. ( 12/2014 - 12/2015)
\item Treasurer, Society of Physics Students. (Fall 2015)
\item Vice President, Society of Physics Students. (2013-2014)
\item Inter-fraternity Council Recruitment Adviser. (2013)
\end{itemize}

{\bf{Activities and Associations}}\\
\begin{itemize}
\setlength\itemsep{0em}
\item LIGO Scientific Collaboration member. (2013 - present)
\item Sigma Pi Sigma (Physics Honor Society).
\item Phi Mu Epsilon (Mathematics Honor Society).
\item Omicron Delta Kappa (National Leadership Honor Society)
\item APS (American Physical Society). (2014-2016)
\item Phi Eta Sigma. (2013-2016)
\item Gamma Sigma Alpha (Greek Academic Honor Society). (2013-2016)
\item Alpha Lambda Delta. (2013-2016)
\item Golden Key Honor Society. (2013-2016)
\item Sigma Alpha Lambda. (2013-2016)
\item National Society of Collegiate Scholars. (2013-2016)
\item The Gamma Beta Phi Society (national honor and service organization). (2012-2015)
\item AAS (American Astronomical Society). (2013-2014)
\end{itemize}

\endinput