\section{\sc Presentations}

%\emph{Educational Data Mining for Online Differentiation of Secondary Mathematics}, Education Symposium, Department of Education, Bates College. (April 2016)

%\emph{Educational Data Mining with Numerical and Categorical Data}, Mount  David Summit, Bates College.  (April 2016)
\emph{Limiting the effects of earthquakes on gravitational-wave interferometers}, LSC-Virgo Meeting, Pasadena, CA. (March 2017)

\emph{LIGO Detector Characterization with 
Genetic Programming}, April APS Meeting, Washington, DC. (January 2017)

\emph{Genetic Programming Applied to Glitch Classification at LIGO}, Computing in High Energy AstroParticle Research Conference, Columbus, OH. (August 2016)

\emph{A low-latency Glitch Classification Algorithm Based in Waveform Morphology for Advanced LIGO}, April APS Meeting, Salt Lake City, UT. (April 2016)

\emph{The Birth of Gravitational-wave Astronomy}, Mississippi State University SPS Invited Talk, Starkville, MS. (March 2016)

\emph{A low-latency Glitch Classification Algorithm Based in Waveform Morphology for Advanced LIGO}, Mississippi Academy of Sciences Meeting, Hattiesburg, MS. (2016)

\emph{Characterization of the Omicron Trigger Generator and Transient analysis of aLIGO Data}, April APS Meeting, Baltimore, MD. (2015)

\emph{A Short Lecture on General Relativity}, Society of Physics Students Zone 10 regional conference, Oxford, MS. (2013)

Live television physics segment (``Spooky Demonstrations'') on WREG News3, Memphis, TN. (2012)


\endinput